Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-23 outputs/paper/paper.qmd
Updated ReadMe Title and rerendered paper

## TTC Bus Delay

@@

## TTC Streetcar Delay

@@

## TTC Subway Delay

### Delay Code
```{r}
#| label: tbl-subway-code
#| tbl-cap: Sample of TTC Subway Delay Code
#| echo: false
#| message: false

>>>>

## TTC Bus Delay {#sec-data-bus}

@@

## TTC Streetcar Delay {#sec-data-streetcar}

@@

## TTC Subway Delay {#sec-data-subway}

### Delay Code {#sec-data-code}
```{r}
#| label: tbl-subway-code
#| tbl-cap: Sample of TTC Subway Delay Code
#| echo: false
#| message: false
